\documentclass{article}
\usepackage[utf8]{inputenc}

\begin{document}
\section{Purpose}
\begin{itemize}
    \item Describe my college experience centered around the quote
    \item Focus on the shifts -- pre-med to CS, within my major, etc
\end{itemize}

\section{Outline}
\subsection{Intro}
\begin{itemize}
    \item I began college thinking I could have it all planned out -- my major, my four-year plan, my 12-year plan, etc. 
    \item However, I happened upon this quote shortly before entering college, and keeping it in mind, I went through a variety of experiences that made me reconsider things.
\end{itemize}
\subsection{Freshman Year} 
\begin{itemize} 
    \item Honors 345: Inspired me to keep digging beneath the surface, not just of Seattle, but also of my own assumptions and beliefs.
    \item COPE Health Scholars (experiential learning): The COPE program was my first real foray into being pre-med. I undertook this to gain invaluable pre-med experience, but ultimately I got tired and realized I didn't want to be pre-med.
    \item Neurobiology Research: I quickly learned that I didn't like doing research either -- at least, specifically not wet lab research. I had to go back to the drawing board in terms of what I wanted.
\end{itemize}
\subsection{Sophomore Year}
\begin{itemize}
    \item I began to challenge myself and really think outside the box 
    \item CSE143X was daunting and scary as I had no previous CS experience. It also turned out to be incredibly rewarding and cement my desire to do CS.
    \item Brunton Lab: This research was much more fulfilling than the last. Working with facial recognition and ECoG data was an amazing marriage of my passions, and allowed me to pursue my interest in both.
\end{itemize}
\subsection{Junior Year}
\begin{itemize}
    \item Just when I was getting the hang of the introductory coursework, I was hit with more challenging courses. These made me consider my path within the major and beyond
    \item Distributed Systems is commonly considered the most difficult and time-consuming class in computer science. In the process, I gained an appreciation for lower-level programming, and found my ideal specialization.
    \item The Amazon internship then gave me the opportunity to put these skills into practice, and work on real products.
\end{itemize}
\subsection{Senior Year}
\begin{itemize}
    \item Cloud capstone: Although the Amazon internship was valuable in expanding my skills and working on real products, I had yet to create a product truly of my own. The cloud capstone
\end{itemize}
\end{document}
